\documentclass[a4paper,11pt]{scrartcl}

%\renewcommand{\arraystretch}{1.5}


%\lvsemester{SS 2021}
%\lvname{Computational Linguistics}
%\zeit{60 minutes}
%\datum{July 21\textsuperscript{th} 2021}

\usepackage{enumitem}

% Load the setspace package
\usepackage{setspace}
% Using \doublespacing in the preamble 
% changes text to double line spacing
\doublespacing


\title{W1 Assignment -- Terminal}
\subtitle{Computational Linguistics}

\author{John Gamboa}
\date{\today}

\setkomafont{author}{\sffamily}
\setkomafont{date}{\sffamily}



\setlength{\parindent}{0pt}

\begin{document}
\maketitle

% !TeX spellcheck = en_US
\section{Command Line}

\subsection{Cmd / Terminal}

(In the following "story", the commands for Mac/Linux and for Windows are
supposed to work)
Assume you just opened your terminal and went to a place containing a folder
called \verb|blah|.

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}

What command do you need to be able to enter the folder \verb|blah| ?

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}

Assume you just ran that command. What command would you need to find out what
is the content of this folder?

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}

Now you want to go back to the folder you were in before. What command would you
need to use?

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}

Assume you just ran that command. Now assume you'd like to create a new folder
called \verb|my_new_folder|. Write the command you'd use to do that.

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}

Let's say you regretted creating this folder and would like to actually delete
it. Write the command you'd use to delete the folder.

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}



\subsection{PATH variable}

Now let's say that you'd like to run the program \verb|my_program| (or, for
Windows users, \verb|my_program.exe|), that is in your \verb|PATH|. What
command would you need to write?

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}
 

And let's say you'd like to print your \verb|PATH| variable. What command
would you need?

%\vspace{0.3cm}
\verb|command|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
%\vspace{0.2cm}
 

\subsection{PATH variable -- What is it?}

One of the following alternatives describes the meaning/use of the PATH variable:

\begin{enumerate}[label=\alph*)]
\onehalfspacing
\item Whenever the operating system (Windows, Linux, Mac) needs to find a
program to be executed, it looks for the program on the \verb|PATH| variable

\item The \verb|PATH| variable indicates the directory where the terminal
is currently located

\item Whenever you use the \verb|cd| command, the \verb|PATH| variable is
the argument passed to \verb|cd|, which indicates where the terminal is supposed
to move to

\item Both the first and the second alternatives are correct
\end{enumerate}

\verb|answer|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_


\section{Course organization}

\subsection{Credit points}

Select the correct alternative:

\begin{enumerate}[label=\alph*)]
\onehalfspacing

\item This course will give you 4 credit points ECTS

\item This course will give you no credit points ECTS

\item This course will give you 3 credit points ECTS

\item John doesn't know how many credit points ECTS this course will give you.
      You should figure this out with your department
\end{enumerate}

\verb|answer|: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\section{What is Computational Linguistics}

\subsection{Multiple choice}

Mark which of the following are foundational fields to Computational
Linguistics:

\begin{itemize}
\item Chemistry

\item Economics

\item Geography

\item Electrical engineering

\item Psychology

\item Philosophy

\item Neuroscience

\item Literary criticism

\item Linguistics

\item Mathematics

\item Computer Science
\end{itemize}

\end{document}

